NMRlipids IV: Headgroup \& glycerol backbone structures, and cation binding in bilayers with PS lipids

### 2018-04-20 Manuscript/manuscriptPS.tex
Update density figures

\begin{figure}[]
  \centering
  \includegraphics[width=8.0cm]{../Figs/CIdensPSOCmixt.eps}
  \caption{  Counterion density distributions from PC:PS mixtures.
\label{CIdensPSOCmixt}
  }
  \todo{Add Berger results.}
\end{figure}

@@

\begin{figure*}[]
  \centering
  \includegraphics[width=18cm]{../Figs/CHANGESwithCaClPS.eps}
  \caption{\label{changesWITHCaClPS}
    POPC (left) and POPS (right) headgroup order parameters in lipid bilayer with POPC:POPS (5:1) mixture
    as a function CaCl$_2$ concentration from experiments \cite{roux90} and different simulations.
  }
  \todo{Upcoming simulations with original CHARMM36 have been mentioned in the blog:
  http://nmrlipids.blogspot.com/2017/12/nmrlipids-iv-current-status-and.html?showComment=1520090718976\#c5569269391707740056} \\
  \todo{Upcoming Lipid17 simulations have been mentioned in the blog
    http://nmrlipids.blogspot.com/2017/12/nmrlipids-iv-current-status-and.html?showComment=1515177306419\#c994825612316235467}
\end{figure*}
\begin{figure}[]
  \centering
  \includegraphics[width=9cm]{../Figs/CAdensPCPSmixture.eps}
  \caption{\label{CAdensPCPSmixture}
    Ca2+ density profiles from simulations.
  }
  \todo{Ca2+ binding in CHARMM is lower than to neutral membrane. The reason should be found out (probably equilibration).}
  \todo{These are now mass densities, numbers would be probably better.}
  \todo{Counterions should be also included.}
  \todo{Not all the data from MacRog is included.}
\end{figure}

>>>>

\begin{figure}[]
  \centering
  \includegraphics[width=8.0cm]{../Figs/CIdensPSOCmixt.eps}
  \caption{  Counterion density distributions from PC:PS mixtures.
\label{CIdensPSOCmixt}
  }
\end{figure}

@@

\begin{figure*}[]
  \centering
  \includegraphics[width=18cm]{../Figs/CHANGESwithCaClPS.eps}
  \caption{\label{changesWITHCaClPS}
    POPC (left) and POPS (right) headgroup order parameters in lipid bilayer with POPC:POPS (5:1) mixture
    as a function CaCl$_2$ concentration from experiments \cite{roux90} and different simulations.
  }
  \todo{Upcoming simulations with original CHARMM36 have been mentioned in the blog:
  http://nmrlipids.blogspot.com/2017/12/nmrlipids-iv-current-status-and.html?showComment=1520090718976\#c5569269391707740056} \\
  \todo{Upcoming Lipid17 simulations have been mentioned in the blog
    http://nmrlipids.blogspot.com/2017/12/nmrlipids-iv-current-status-and.html?showComment=1515177306419\#c994825612316235467}
\end{figure*}
\begin{figure}[]
  \centering
  \includegraphics[width=9cm]{../Figs/CAdensPCPSmixture.eps}
  \caption{\label{CAdensPCPSmixture}
    Ca2+ density profiles from simulations.
  }
  \todo{The CHARMM results are mass densities, numbers should be used.} \\
  \todo{Should we include also counterions into the plot?} \\
  \todo{Not all the data from MacRog is included.} 
\end{figure}
